Insilico Splits

### 2018-03-16 Insilico Splits.Rmd
...

all.patient.info = read.patient.info(patient.file, demo.file, set='all')$info
head(all.patient.info)

@@

cache.dir = paste(data, 'Analysis', sub('\\+','',paste(tile.w, collapse='_')), sep='/')

ins_splits = grep('val_', list.dirs(cache.dir), value=T)

performance = data.frame()
rocs = list()

select.alpha = '0.9'

file = paste(cache.dir, 'insilico_splits.Rdata', sep='/')
if (file.exists(file)) {
  load(file, verbose=T)
  rocs = insilico.rocs
  performance = insilico.perf
} else {
  for (split in ins_splits) {
    load(grep('all.*Rdata', list.files(split,full.names = T), value=T), verbose=F)
    performance = rbind(performance, performance.at.1se[[select.alpha]])
    rm(plots,coefs,performance.at.1se,models,cv.patient)

    load(grep('loo.*Rdata', list.files(split,full.names = T), value=T), verbose=F)
    rm(plots, performance.at.1se,coefs,nzcoefs,fits)

@@

    preds = do.call(rbind.data.frame, lapply(pg.samp, function(df) df[c('Status','Prediction')]))
    roc = pROC::roc(Status ~ Prediction, data=preds, auc=T, ci=T, of='thresholds')
    #rocs = rbind(rocs,c(ci.auc(roc), coords(roc, 'best') ))
    roc$model = 'in-silico'
    roc$is = basename(split)
    rocs[[basename(split)]] = roc

@@

  insilico.rocs=rocs
  insilico.perf=performance
  save(insilico.rocs, insilico.perf, file=paste(cache.dir, 'insilico_splits.Rdata', sep='/'))
}

load(grep('all.*Rdata',list.files(cache.dir, full.names = T), value=T), verbose=F)
performance = rbind(performance, performance.at.1se[[select.alpha]])
performance$split = c(basename(ins_splits), 'discovery')
rm(plots,coefs,performance.at.1se,models,cv.patient,dysplasia.df,labels)

load(grep('loo\\.Rdata', list.files(cache.dir,full.names = T), value=T), verbose=F)
rm(plots, performance.at.1se,coefs,nzcoefs,fits)

@@

  ggplot(df, aes(Specificity, Sensitivity,color=is)) + geom_line(size=1) + 
    geom_line(data=subset(df, model == 'discovery'), color='red', size=1) +
    scale_x_reverse() +
    scale_color_brewer(palette='Blues') +
    labs(title=title, x='Specificity (FPR)', y='Sensitivity (TPR)')  + plot.theme +
    theme(legend.position = 'none')
}

>>>>

all.patient.info = read.patient.info(patient.file, demo.file, set='all')$info

@@

#cache.dir = paste(data, 'Analysis', sub('\\+','',paste(tile.w, collapse='_')), sep='/')
model.dir = paste(data, 'Analysis/5e6_arms_all_exAHM0320', sep='/')
split.dir = '/Volumes/research1/gerstung/skillcoyne/Ellie/Analysis/5e6_arms_splits_exAHM0320'

performance = data.frame(); rocs = list()
select.alpha = '0.9'

file = paste(model.dir, 'insilico_splits.Rdata', sep='/')
if (file.exists(file)) {
  load(file, verbose=T)
  rocs = insilico.rocs
  performance = insilico.perf
} else {

  split.dirs = list.files(split.dir, full.names = T)
  for (split in 1:length(split.dirs)) {
    print(split)  
    load(list.files(split.dirs[split],full.names = T, pattern='all.*Rdata'), verbose=T)
    performance = rbind(performance, performance.at.1se[[select.alpha]])
    rm(plots,coefs,performance.at.1se,models,cvs)

    load(list.files(split.dirs[split],full.names = T, pattern='loo.*Rdata'), verbose=T)
    rm(plots, performance.at.1se,coefs,nzcoefs,fits)

@@

    preds = do.call(rbind.data.frame, lapply(pg.samp, function(df) df[c('Status','Prediction')]))
    roc = pROC::roc(Status ~ Prediction, data=preds, auc=T, ci=T, of='thresholds')
    #rocs = rbind(rocs,c(ci.auc(roc), coords(roc, 'best') ))
    roc$model = 'in-silico'
    roc$is = split
    rocs[[split]] = roc

@@

  insilico.rocs=rocs
  insilico.perf=performance
  save(insilico.rocs, insilico.perf, file=paste(model.dir, 'insilico_splits.Rdata', sep='/'))
}

n.splits = nrow(performance)

load(list.files(model.dir, full.names = T, pattern = 'all.*Rdata'))

performance = rbind(performance, performance.at.1se[[select.alpha]])
performance$split = c(paste('split',1:n.splits,sep='.'), 'discovery')
rm(plots,coefs,performance.at.1se,models,cvs,dysplasia.df,labels)

load(list.files(model.dir,full.names = T, pattern='loo.Rdata'))
rm(plots, performance.at.1se,coefs,nzcoefs,fits)

@@

  ggplot(df, aes(Specificity, Sensitivity,color=is)) + geom_line(size=1) + 
    geom_line(data=subset(df, model == 'discovery'), color='red', size=1) +
    scale_x_reverse() +
    scale_color_brewer(palette='Blues') +
    labs(title='', x='Specificity (FPR)', y='Sensitivity (TPR)')  + plot.theme +
    theme(legend.position = 'none')
}
